Supplementary Material for Asymmetry paper

### 2020-05-01 Supplementary/Sup_mat.Rmd
Big update
Loads of updates to the figures in particular

# plot samples in terms of difference? 
plt_hdi <- df_sample %>% 
  filter(n_trials != 12) %>%
  mutate(diff = baseline - comparison) %>% 
  group_by(n_subs, dist_type) %>% 
  summarise(mu = mean(diff),
            upper = hdi(diff)[2],
            lower = hdi(diff)[1]) %>% 
  ggplot(aes(n_subs, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower, ymax = upper),
              alpha = .3) + 
  facet_wrap(~dist_type) + 
  theme_bw() + 
  scale_x_continuous("Sample Size") + 
  scale_y_continuous("Difference: Athletes - Avatar")

@@

```
The results of this model suggest that our participants were sensitive to the probability information (see above figure). In the Biased condition, the average participant fixated the most likely target `r paste(round(HDI_Bias[1,3], digits = 3)*100, "%", sep = "")` of the time (95% HDPI of |`r paste(round(HDI_Bias[1,2], digits = 3)*100, "%", sep = "")`, `r paste(round(HDI_Bias[1,4], digits = 3)*100, "%", sep = "")`|), compared to `r paste(round(HDI_Bias[2,3], digits = 3)*100, "%", sep = "")` (95% HPDI of |`r paste(round(HDI_Bias[2,2], digits = 3)*100, "%", sep = "")`,`r paste(round(HDI_Bias[2,4], digits = 3)*100, "%", sep = "")`|) in the symmetric condition. The width of these intervals reflects a high degree of uncertainty in fixed effects, due to the range of behaviours exhibited by participants. None-the-less, the HPDI on the difference between these two conditions, |`r round(D_bias_lower, digits = 3)`, `r round(D_bias_upper, digits = 3)`| is largely positive and we can be reasonably confident (P(difference > 0 | data ) =  `r round(p_bias_bigger, digits = 3)`) that the most-likely target is fixated more frequently in the biased condition. The distance between the square targets did not appear to have any consistent effect in the Symmetric condition, however there was a small decrease in fixations towards the “most likely” box when the boxes were far apart in the bias condition (dropping from `r round(HDI_interaction[1,4], digits = 3)`%, 95% HPDI of |`r round(HDI_interaction[1,3], digits = 3)`%,`r round(HDI_interaction[1,5], digits = 3)`%| to `r round(HDI_interaction[2,4], digits = 3)`%, 95% HPDI of |`r round(HDI_interaction[2,3], digits = 3)`%,`r round(HDI_interaction[2,5], digits = 3)`%|). As such, the difference between the conditions were much more pronounced in the close condition (P(Bias > Symmetric|data)) = `r round(Diff_Interaction_compbias[1,2], digits = 3)`%) than in the far condition (P(Bias > Symmetric|data)) = `r round(Diff_Interaction_compbias[2,2], digits = 3)*100`%). The width of these intervals reflects the range of performance that was exhibited by participants. However, this does show that participants generally made us of this probability information in order to decide where to fixate.

```{r model for side fixations, echo = F, include = F}
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_S_dt")
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_S_dt_draws")
df_prop_S <- fix_S_post$draws_df %>% 
  mutate(prop = boot::inv.logit(estimate))
```

@@

```{r get HDPI values, echo = F, include = F}
```

We can now ask whether participants were more likely to make use of the optimal strategy when in the biased condition. We will use the same predictors as above, but this time, to predict the probability of participants fixating either of side boxes over the central box. A random observer, equally likely to look at any of the three boxes, would have a 66% chance of fixating a Side box. The results suggest that in the Biased condition, participants were more likely to fixate the side boxes than the central box in both the close (95.4%,HPDI of |85.9%, 99.9%|) and far (96.4%, HPDI of |86.9%, 100%|) conditions. This contrasts with  than when the participants were in the Symmetric condition (close; 83.9%, 95% HPDI of |60.3%, 98.5%|) for the close, and , far; 84.7%,( 95% HPDI of |62.8%, 99.9%|) for the far apart targets in the symmetric condition. These results would suggest that the bias present in the Biased condition encouraged participants to fixate the side boxes more often. However, it does not suggest that adding this bias facilitated the use of the optimal strategy as participants did not appear to account for distance in an optimal manner.

>>>>

# plot samples in terms of difference? 
plt_hdi <- df_sample %>% 
  filter(n_trials != 12,
         n_subs != 2) %>%
  mutate(diff = baseline - comparison) %>% 
  group_by(n_subs, dist_type) %>% 
  summarise(mu = mean(diff),
            upper = hdi(diff)[2],
            lower = hdi(diff)[1]) %>% 
  ggplot(aes(n_subs, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower, ymax = upper),
              alpha = .3) + 
  facet_wrap(~dist_type) + 
  theme_bw() + 
  scale_x_continuous("Sample Size") + 
  scale_y_continuous("Difference: Athletes - Avatar")

@@

```
The results of this model suggest that our participants were sensitive to the probability information (see above figure). In the Biased condition, the average participant fixated the most likely target `r paste(round(HDI_Bias[1,3], digits = 3)*100, "%", sep = "")` of the time (95% HDPI of |`r paste(round(HDI_Bias[1,2], digits = 3)*100, "%", sep = "")`, `r paste(round(HDI_Bias[1,4], digits = 3)*100, "%", sep = "")`|), compared to `r paste(round(HDI_Bias[2,3], digits = 3)*100, "%", sep = "")` (95% HPDI of |`r paste(round(HDI_Bias[2,2], digits = 3)*100, "%", sep = "")`,`r paste(round(HDI_Bias[2,4], digits = 3)*100, "%", sep = "")`|) in the symmetric condition. The width of these intervals reflects a high degree of uncertainty in fixed effects, due to the range of behaviours exhibited by participants. None-the-less, the HPDI on the difference between these two conditions, |`r round(D_bias_lower, digits = 3)*100`, `r round(D_bias_upper, digits = 3)*100`| is largely positive and we can be reasonably confident (P(difference > 0 | data ) =  `r round(p_bias_bigger, digits = 3)*100`) that the most-likely target is fixated more frequently in the biased condition. The distance between the square targets did not appear to have any consistent effect in the Symmetric condition, however there was a small decrease in fixations towards the “most likely” box when the boxes were far apart in the bias condition (dropping from `r round(HDI_interaction[1,4], digits = 3)*100`%, 95% HPDI of |`r round(HDI_interaction[1,3], digits = 3)*100`%,`r round(HDI_interaction[1,5], digits = 3)*100`%| to `r round(HDI_interaction[2,4], digits = 3)*100`%, 95% HPDI of |`r round(HDI_interaction[2,3], digits = 3)`%,`r round(HDI_interaction[2,5], digits = 3)*100`%|). As such, the difference between the conditions were much more pronounced in the close condition (P(Bias > Symmetric|data) = `r round(Diff_Interaction_compbias[1,2], digits = 3)*100`%) than in the far condition (P(Bias > Symmetric|data) = `r round(Diff_Interaction_compbias[2,2], digits = 3)*100`%). The width of these intervals reflects the range of performance that was exhibited by participants. However, this does show that participants generally made us of this probability information in order to decide where to fixate.

```{r model for side fixations, echo = F, include = F}
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_S_dt")
load("../Analyses/Experiment_4_Prob/modelling/BRMS/model_output/bm_fix_S_dt_draws")
df_prop_S <- fix_S_post$draws_df %>% 
  mutate(prop = boot::inv.logit(estimate)) %>% 
  select(-estimate)
```

@@

```{r get HDPI values, echo = F, include = F}
HDI_side_Bias <- df_prop_S %>% 
  group_by(Bias_type) %>% 
  summarise(lower = hdci(prop)[,1],
            mu = mean(prop),
            upper = hdci(prop)[,2])

HDI_side_dist <- df_prop_S %>% 
  group_by(Dist_type) %>%  
  summarise(lower = hdci(prop)[,1],
            mu = mean(prop),
            upper = hdci(prop)[,2])

HDI_side_interaction <- df_prop_S %>%
  group_by(Bias_type, Dist_type) %>%  
  summarise(lower = hdci(prop)[,1],
            mu = mean(prop),
            upper = hdci(prop)[,2])
```

We can now ask whether participants were more likely to make use of the optimal strategy when in the biased condition. We will use the same predictors as above, but this time, to predict the probability of participants fixating either of side boxes over the central box. A random observer, equally likely to look at any of the three boxes, would have a 66% chance of fixating a Side box. The results suggest that in the Biased condition, participants were more likely to fixate the side boxes than the central box in both the close (`r round(HDI_side_interaction[1,4], digits = 3)*100`%, HDPI of |`r round(HDI_side_interaction[1,3], digits = 3)*100`%, `r round(HDI_side_interaction[1,5], digits = 3)*100`%|) and far (`r round(HDI_side_interaction[2,4], digits = 3)*100`%, HDPI of |`r round(HDI_side_interaction[2,3], digits = 3)*100`%, `r round(HDI_side_interaction[2,5], digits = 3)*100`%|) conditions. This contrasts with  than when the participants were in the Symmetric condition (`r round(HDI_side_interaction[3,4], digits = 3)*100`%, HDPI of |`r round(HDI_side_interaction[3,3], digits = 3)*100`%, `r round(HDI_side_interaction[3,5], digits = 3)*100`%|) for the close, and , far; `r round(HDI_side_interaction[4,4], digits = 3)*100`%, HDPI of |`r round(HDI_side_interaction[4,3], digits = 3)*100`%, `r round(HDI_side_interaction[4,5], digits = 3)*100`%|) for the far apart targets in the symmetric condition. These results would suggest that the bias present in the Biased condition encouraged participants to fixate the side boxes more often. However, it does not suggest that adding this bias facilitated the use of the optimal strategy as participants did not appear to account for distance in an optimal manner.
